CSD, Disjoint components and trayectory detection

### 2019-11-07 ArticuloCSDyCM/Paper03.tex
figuras facilitadas incorporadas

\usepackage{graphicx}
\usepackage{longtable}

@@

\begin{figure}
  \includegraphics[width=0.9\textwidth]{Figuras/lfpevocado01.pdf}
  \caption{A set of frames showing the stimulus and posterior activity.
    The frame titled ``0 ms'' is just before the stimulus was
    made.  A diagram of the Granular and Pyramidal Layers is shown
    against the noice background. The black rectangle delimites the
    r.o.i. and the black arrow shows the site of stimulation in GD.
  }\label{lfpevocada}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.9\textwidth]{Figuras/lfpcsdcm01.pdf}
\caption{ Comparison of the activity represented as LFP, CSD and CM.
  The time after
  stimulation in ms is shown in the central column for each row.
  In this series of frames a relatively big patch of the electrodes
  still appear saturated, but even so the CSD shows good localization
  of the relevant deflections from the neutral or noise base signal.
  The CM representation concentrates the locus of action even more.
  The circular dots in the third column represent the center of mass
  of coherent active subsets.
}\label{lfpcsdcm}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.9\textwidth]{Figuras/lfpcsdcm02.pdf}
\caption{ The same as previous figure, but focusing on the
  region of interest, including the stratum pyramidale of CA3.
}\label{lfpcsdcmsub}
\end{figure}

@@

\begin{figure}[h]
 \includegraphics[width=0.9\textwidth]{Figuras/CMVariousTimes01.pdf}
  \caption{ The CM analysis over the same images as figure \ref{lfpcsdcmsub} C. Some trajectories
    are calculated before the 4ms time stamp. The triangular mark shows the later point of the
    trajectory, either the end or the last calculated position until that moment. The circular
    mark is the start of the trajectory. We can see that activity moves form CA3 distal to
    proximal in alternating waves of action (hiperpolarization, firing and repolarization).
  }\label{cmevocada}
\end{figure}

\begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{./Figuras/trayevocadasub01.pdf}
  \caption{The evoked trajectories in the r.o.i. We begin to track them
    at the 0.9 ms mark, after letting the saturation of the stimulus recede.
    At 3ms a very clear sink trajectory is moving retrogradly towards CA2,
    sheepherd by two shorter source trayectories. At 5.6 a depolarization
    trajectory starts, following almost the same path and presenting also its
    two companions, ending around the 7.7ms timestamp. No significant
  trajectories are observed after the 10ms mark. }\label{trayevo}
\end{figure}

\subsection{Application to facilitated activity}

@@

\begin{figure}
  \includegraphics[width=0.9\textwidth]{./Figuras/LFPvsCSD_4AP.pdf}
  \caption{Comparison of LFP and CSD representations
    at the moments of the epileptic burst. In the first row
    we present the data as measured, no denoising or filtering has
    been applied. The units of measurement are in $\muV{}$. In
    the middle row a direct application of a difference operator
    gives us the CSD. This sort of operators are very sensitive
    to noise, in this case, spatial hard edges, which become
    greatly exaggerated. In the third row we present the same
    data after a Gaussian spatial filter ( Gaussian Blur) has
    been applied. }\label{lfpycsd4ap}
\end{figure}

\begin{figure}
  \includegraphics[width=0.9\textwidth]{./Figuras/Fronteras2sigma.pdf}
  \caption{The detection of disconnected components for the Sink and Source
    Sets. We take the the threshold value as two times the
    standard deviation of the whole data in CSD representation. In
    the upper row the data without the Gaussian Blur filtering is shown.
    Although the location of some of the active sets is clear, a lot of the
    joint activity gets hidden under the spatial noise. In the lower
    row we repeat the detection with the smoothed data. Large, coherent
    patches of activity are clearly shown, and the structure of the
    stratum pyramidale is apparent. 
  }\label{csdfrontera}
\end{figure}

\begin{figure}
  \includegraphics[width=0.9\textwidth]{./Figuras/SeqTray4AP01.pdf}
  \caption{ The activity in the Center of Mass and Trajectories representation.
    A single epileptic attack is shown from slightly before the onset until the
    last wave of the attack. Sink and Source trajectories are shown in blue
    and red, respectively. In order to not saturate the latter subfigures
    we take a persistence value of 2 ms, meaning that we do not shown
    trajectories 2 ms after they have ended.}\label{tray4ap}.
 \end{figure}

\subsection{Application to spontaneous activity in idem.}

We had one experiment in which we could trace very nicely the data on DG and CA simultaneously without adding excitatory drugs.

>>>>

\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}

@@

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{Figuras/lfpevocado01.pdf}
  \caption{A set of frames showing the stimulus and posterior activity.
    The frame titled ``0 ms'' is just before the stimulus was
    made.  A diagram of the Granular and Pyramidal Layers is shown
    against the noice background. The black rectangle delimites the
    r.o.i. and the black arrow shows the site of stimulation in GD.
  }\label{lfpevocada}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_completa_evocada3R7.pdf}
\caption{ Comparison of the activity represented as LFP, CSD and CM.
  The time after
  stimulation in ms is shown in the central column for each row.
  In this series of frames a relatively big patch of the electrodes
  still appear saturated, but even so the CSD shows good localization
  of the relevant deflections from the neutral or noise base signal.
  The CM representation concentrates the locus of action even more.
  The circular dots in the third column represent the center of mass
  of coherent active subsets.
}\label{lfpcsdcm}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_sub_evocada3R7.pdf}
\caption{ The same as previous figure, but focusing on the
  region of interest, including the stratum pyramidale of CA3. A different
  color scheme was choosen on the last column, so as to provide borders
  that show how the disconnected componentes where choosen. 
}\label{lfpcsdcmsub}
\end{figure}

@@

%\begin{figure}[h]
% \includegraphics[width=0.9\textwidth]{Figuras/CMVariousTimes01.pdf}
%  \caption{ The CM analysis over the same images as figure \ref{lfpcsdcmsub}. Some trajectories
%    are calculated before the 4ms time stamp. The triangular mark shows the later point of the
%    trajectory, either the end or the last calculated position until that moment. The circular
%    mark is the start of the trajectory. We can see that activity moves form CA3 distal to
%    proximal in alternating waves of action (hiperpolarization, firing and repolarization).
%  }\label{cmevocada}
%\end{figure}

\begin{figure}[H]
 \includegraphics[width=0.7\textwidth]{./Figuras/trayevocadasub.pdf}
  \caption{The evoked trajectories in the r.o.i. We begin to track them
    at the 0.9 ms mark, after letting the saturation of the stimulus recede.
    At 3ms a very clear sink trajectory is moving retrogradly towards CA2,
    sheepherd by two shorter source trayectories. At 5.6 a depolarization
    trajectory starts, following almost the same path and presenting also its
    two companions, ending around the 7.7ms timestamp. No significant
  trajectories are observed after the 10ms mark. }\label{evotracks}
\end{figure}

\subsection{Application to facilitated activity through injury}

The facilitated activity through a small injury produces very clean
and ordered activity in the CA layers, as measured by the CM analysis.
The results can be seen in the figures
\ref{diagfaci}, \ref{lfpcsdcmfaci}, \ref{facitracks} and
\ref{facitracktodas}.
A previous diagram is on the figure \ref{diagfaci}.

\begin{figure}[H]
  \includegraphics[width=0.7\textwidth]{Figuras/diagfacilitada.pdf}
  \caption{A diagram of the approximate location of the pyramidal and granular strata on the hippocampus slice, during a peak of activity as measured in \muV{}.
  }
  \label{diagfaci}
\end{figure}

\begin{figure}[H]
\includegraphics[width=0.7\textwidth]{Figuras/lfpcsdcm_facilitada.pdf}
\caption{ Comparison of the activity represented as LFP, CSD and CM,
  in the same style as fig. \ref{lfpcsdcm}, but for facilitated activity.
  In this case the time counter starts at some moment around 80 ms. before the
  onset of the burst of activity.
}\label{lfpcsdcmfaci}
\end{figure}

\begin{figure}[H]
 \includegraphics[width=0.7\textwidth]{./Figuras/trayfaciljuntas.pdf}
 \caption{The trajectories for  the facilitated activity, in
 sequence of aparition around the burst of action.}\label{facitracks}
\end{figure}

\begin{figure}[H]
 \includegraphics[width=0.7\textwidth]{./Figuras/traytodasfacilitada.png}
 \caption{The trajectories for  the facilitated activity, shown
 all together.}\label{facitracktodas}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{./Figuras/LFPvsCSD_4AP.pdf}
  \caption{Comparison of LFP and CSD representations
    at the moments of the epileptic burst. In the first row
    we present the data as measured, no denoising or filtering has
    been applied. The units of measurement are in $\muV{}$. In
    the middle row a direct application of a difference operator
    gives us the CSD. This sort of operators are very sensitive
    to noise, in this case, spatial hard edges, which become
    greatly exaggerated. In the third row we present the same
    data after a Gaussian spatial filter ( Gaussian Blur) has
    been applied. }\label{lfpycsd4ap}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{./Figuras/Fronteras2sigma.pdf}
  \caption{The detection of disconnected components for the Sink and Source
    Sets. We take the the threshold value as two times the
    standard deviation of the whole data in CSD representation. In
    the upper row the data without the Gaussian Blur filtering is shown.
    Although the location of some of the active sets is clear, a lot of the
    joint activity gets hidden under the spatial noise. In the lower
    row we repeat the detection with the smoothed data. Large, coherent
    patches of activity are clearly shown, and the structure of the
    stratum pyramidale is apparent. 
  }\label{csdfrontera}
\end{figure}

\begin{figure}[H]
  \includegraphics[width=0.9\textwidth]{./Figuras/SeqTray4AP01.pdf}
  \caption{ The activity in the Center of Mass and Trajectories representation.
    A single epileptic attack is shown from slightly before the onset until the
    last wave of the attack. Sink and Source trajectories are shown in blue
    and red, respectively. In order to not saturate the latter subfigures
    we take a persistence value of 2 ms, meaning that we do not shown
    trajectories 2 ms after they have ended.}\label{tray4ap}.
 \end{figure}
